% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{multicol}
\usepackage{enumitem}
\setlength{\textwidth}{5.1in} % set width of text portion

\renewcommand{\baselinestretch}{0.76}\normalsize

\begin{document}
%\addtolength{\topmargin}{-0.5in}
% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\Large\bf Daniel Kolbman}
 \moveleft.5\hoffset\centerline{(267) 261-4552 - dan@kolbman.com} \moveleft.5\hoffset\centerline{kolbman.com - github.com/dankolbman}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% \address{\bf ADDRESS \\ }

\begin{resume}

%%%%% EDUCATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{EDUCATION}
  {\sl Bachelor of Science,} Physics, Mathematics Minor \\
  Rochester Institute of Technology, 2015	\\

%%%%% PROFESSIONAL EXPERIENCE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROFESSIONAL\\EXPERIENCE}

  {\sl Software Engineer} \hfill            Spring 2016- \\
  {\sl University of Chicago Center for Data Intensive Science}\\
  \begin{itemize}
    \item Worked on a small team of developers in an agile environment to create the Genomic Data Commons.
    \item Investigated, designed, and lead development of a distributed and scalable ETL service for supporting new visualization features using Spark and Elasticsearch.
    \item Imported and managed petabyte-scale, cancer-genomics data in a highly-relational graph data model implemented in PostgreSQL.
    \item Responsible for communicating and collaborating across teams to lay out development effort for significant data model and system design changes.
    \item Conducted interviews and technical screens for a variety of technical positions and helped to onboard new developers.
  \end{itemize}

%  {\sl Systems Administrator} \hfill            Fall, 2012-Spring, 2015 \\
%  {\sl Chester F. Carlson Center for Imaging Science, RIT}\\
%  \begin{itemize}
%    \item Responsible for the maintenance of faculty and lab computers
%      at the Center for Imaging Science.
%    \item Update and configure software required for Imaging Science courses
%      and provide assistance to professors with software and technical problems.
%  \end{itemize}

%%%%% PROJECTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROJECTS}
  {\sl \textbf{More projects and contributions at github.com/dankolbman}}\\
   {\sl Cryptocurrency Algorithm Platform} \hfill            Spring, 2017- \\
  \begin{itemize}
    \item Created a distributed and scalable platform for developing and deploying trading strategies for cryptocurrency markets.
    \item Gathered realtime data from several sources such as exchanges and social media and processed it using Airflow pipelines across a Celery worker pool.
    \item Used Elasticsearch to store historical data for backtesting and analysis.
  \end{itemize}
  {\sl Kaggle} \hfill            Winter, 2015- \\
  \begin{itemize}
    \item Placed in the top 5\% in the Home Depot Product Search Relevance competition utilizing ensembles consisting of tree based, SVM, and neural network models and many NLP tasks for feature extraction and engineering.
    \item Placed top 14\% in the Prudential Life Insurance Assessment competition using a distributed grid search to optimize xgboost hyper-parameters.
    \item Participated in the Bosch Production Line Performance competition with a focus on creating a pipeline that would allow rapid iteration on methods of feature engineering and model parameters.
  \end{itemize}
  {\sl Travel Blog} \hfill            Spring, 2015-Summer, 2015 \\
  \begin{itemize}
    \item Created a blogging platform using the Flask web framework and PostgreSQL with PostGIS to store location data.
    \item Developed an Android companion application to track cell phone GPS data
      and upload it to the Flask application through a REST API.
  \end{itemize}
      
%  {\sl CleverTind} \hfill            Winter, 2014 \\
%  \begin{itemize}
%    \item Created a bot in ruby to interact with a popular dating service and hold
%      conversations with users using a chatbot.
%    \item Used OpenCV to apply facial recognition and construct composite faces and
%      numpy and matplotlib for user analysis.
%  \end{itemize}


%%%%% RESEARCH EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{RESEARCH\\EXPERIENCE}
  {\sl Cancer Cell Migration in 2D and 3D} \hfill  Summer, 2014-Spring 2015\\
  {\sl Adviser: Moumita Das}\\                
  \begin{itemize}
    \item Developed simulation software in Julia and Python for the investigation of cancer cell migration and segregation.
    \item Increased performance by 10-100 times over previous techniques by implementing new collision models in Julia and distributing work across an HPC cluster.
    \item Performed statistical investigation of data using numpy, pandas, matplotlib, and seaborn libraries for Python.
  \end{itemize}
     


%%%%% REFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{REFERENCES}
%\textit{Available upon request}

\end{resume}
\end{document}
